\nomenclature[gp]{$\phi_\alpha$}{Volume fraction of constituent $\alpha$.}
\nomenclature[gr]{$\rho_\alpha$}{Apparent density of constituent $\alpha$.}
\nomenclature[go]{$\mathd \Omega,\ \mathd \Omega_\alpha$}{Volume element of the mixture and constituent $\alpha$, respectively.}
\nomenclature[gr]{$\rho_{\alpha R}$}{Real density of constituent $\alpha$.}
\nomenclature[oh]{$\hat{(\bullet)}_\alpha$}{Production term of quantity $(\bullet)_\alpha$ due to local interaction with other constituents.}
\nomenclature[rv]{$\mbf{v}_\alpha$}{Velocity of phase $\alpha$.}
\nomenclature[od]{$\ds \mtd{\alpha}{(\bullet)}$, $(\bullet)'_\alpha$}{Material time derivative of $(\bullet)$ following the motion of phase $\alpha$.}
\nomenclature[od]{$\mdiv$}{Spatial divergence operator.}
\nomenclature[og]{$\grad$}{Spatial gradient operator.}
\nomenclature[rf]{$\mbf{F}_\alpha$}{Deformation gradient of phase $\alpha$.}
\nomenclature[rl]{$\mbf{l}_\alpha$}{Spatial velocity gradient of phase $\alpha$.}
\nomenclature[rj]{$J_\alpha$}{Determinant of the deformation gradient: $\det \mbf{F}_\alpha$.}
%\nomenclature[rq]{$q_R$}{Reaction rate.}
\nomenclature[rd]{$\mbf{D}$}{Diffusivity tensor.}
\nomenclature[gg]{$\mathd \Gamma$}{Area element.}
\nomenclature[rb]{$\mbf{b}_\alpha$}{External body force on phase $\alpha$.}
\nomenclature[rt]{$\mbf{t}_\alpha$}{Surface traction on phase $\alpha$.}
\nomenclature[rn]{$\mbf{n}$}{Outward unit normal vector.}
\nomenclature[rr]{$r_\alpha$}{Heat source/sink per unit mass associated with phase $\alpha$.}
\nomenclature[rq]{$\mbf{q}_\alpha$}{Heat flux vector associated with phase $\alpha$.}
\nomenclature[ru]{$u_\alpha$}{Specific inner energy of phase $\alpha$.}
\nomenclature[ge]{$\eta_\alpha$}{Specific entropy associated with phase $\alpha$.}
\nomenclature[rt]{$T_\alpha$}{Temperature of phase $\alpha$.}
\nomenclature[gp]{$\psi_\alpha$}{Specific Helmholtz free energy of phase $\alpha$.}
\nomenclature[oaa]{$\mbf{a} \cdot \mbf{b}$}{Dot product of $\mbf{a}$ and $\mbf{b}$.}
\nomenclature[oab]{$\mbf{A} \dcdot \mbf{B}$}{Double contraction of $\mbf{A}$ and $\mbf{B}$.}
\nomenclature[gm]{$\mu_\alpha$}{Gibbs free enthalpy.}
\nomenclature[gs]{$\mbfs{\sigma}_\alpha$}{Cauchy stress tensor of phase $\alpha$.}
\nomenclature[gse]{$\mbfs{\sigma}^E_\alpha$}{Cauchy extra stress tensor of phase $\alpha$.}
\nomenclature[gl]{$\mbfs{\lambda}_\alpha$}{Heat conductivity tensor of phase $\alpha$.}
%\nomenclature[rr]{$R_s$}{Specific gas constant.}
\nomenclature[rw]{$\mbf{w}_{\zeta}$}{Seepage velocity of constituent $\zeta$ relative to solid.}
\nomenclature[rw]{$\tilde{\mbf{w}}_{\zeta}$}{Filter velocity of constituent $\zeta$ relative to solid.}
\nomenclature[rk]{$\mbf{k}$}{Hydraulic permeability with units of [m$^\mathrm{4}$N$^\mathrm{-1}$s$^\mathrm{-1}$].}
\nomenclature[rks]{$\mbf{k}_S$}{Intrinsic permeability with units of [m$^\mathrm{2}$].}
\nomenclature[rcv]{$c_{\bar{v}}$}{Specific heat capacity at constant specific volume.}
\nomenclature[rcp]{$c_{p}$}{Specific heat capacity at constant pressure.}
\nomenclature[rv]{$\bar{v}$}{Specific volume.}
\nomenclature[rxm]{$x_{m\zeta}$}{Mass fraction of constituent $\zeta$ in gas phase.}
\nomenclature[rxn]{$x_{n\zeta}$}{Mole fraction of constituent $\zeta$ in gas phase.}
\nomenclature[rd]{$\mbf{d}_{\zeta}$}{Diffusion velocity of constituent $\zeta$ in gas phase.}
%\nomenclature[rp]{$\hat{\mbf{p}}_\alpha$}{Direct momentum production in phase $\alpha$.}
%\nomenclature[ge]{$\hat{\epsilon}_\alpha$}{Direct energy production in phase $\alpha$.}
\nomenclature[gmv]{$\mu_V$}{Viscosity of the gas.}
\nomenclature[rh]{$h_\alpha$}{Specific enthalpy.}
\nomenclature[rca]{$c_G$, $c_\zeta$}{Concentration of the gas or a gas component.}
\nomenclature[rda]{$\mbf{d}_{\alpha}$}{Rate of deformation tensor.}
\nomenclature[rn]{$n_\zeta$}{Number of moles of component $\zeta$.}
\nomenclature[rm]{$M_\zeta$}{Molar mass of component $\zeta$.}
\nomenclature[ri]{$\mbf{I}$}{Second order unity tensor.}
\nomenclature[rc]{$\mbf{C}_\alpha$}{Right Cauchy-Green tensor of phase $\alpha$.}
\nomenclature[ra]{$\mbf{a}_\alpha$}{Acceleration of phase $\alpha$.}
\nomenclature[od]{$(\bullet)^D$}{Deviatoric part of $(\bullet)$.}
\nomenclature[rf]{$\widetilde{\mbf{F}}_\alpha$}{Isochoric part of the deformation gradient.}
\nomenclature[rc]{$\widetilde{\mbf{C}}_\alpha$}{Isochoric part of the right Cauchy-Green tensor.}
\nomenclature[rr]{$R$}{Universal gas constant.}
\nomenclature[gb]{$\beta_p$}{Isothermal compressibility coefficient.}
\nomenclature[ga]{$\alpha_T$}{Isobaric thermal expansivity coefficient.}
\nomenclature[rna]{$N^a$; $\mbf{N}$}{Shape function of node a; vector/matrix of shape functions.}




